The \project{unRAVE} catalog

### 2016-09-08 article/unrave.tex
Include error floor figures

We calculated all possible pair-wise differences between the labels we
derived from multiple visits.  If \rave\ observed a star $H$ times, there 
are $H!/2(H-2)!$ possible $a$-$b$ pair-wise combinations where we can calculate 
the difference between the derived label (for example, $\logg$) over the
quadrature sum of their formal uncertainties,
\begin{eqnarray}
\eta_{\logg} & = & \frac{\logg_a - \logg_b}{\sqrt{\sigma_{\logg,a}^2 + \sigma_{\logg,b}^2}} \quad .
\end{eqnarray}

If our derived labels and formal errors were correct, the distribution of
$\eta$ values would represent a normal distribution with zero mean and
unity variance.  However, our formal errors are likely to be under-estimated,
and therefore we introduce a systematic error floor for each label, which
is added in quadrature to every observation such that for $\logg$,
\begin{eqnarray}
	\eta_{\logg} & = & \frac{\logg_a - \logg_b}{\sqrt{(\sigma_{\logg,a} + \sigma_{\logg,floor})^2 + (\sigma_{\logg,b} + \sigma_{\logg,floor})^2}} \quad .
\end{eqnarray}

We increased the minimum label error until the distribution of $\eta$ 
values for a given label approximately reached unity.  The minimum error
values for each label are shown with the distribution of (new) $\eta$
values in Figure \ref{fig:pairwise-comparison}.  These minimum values form
part of our error model, and \emph{have} been added in quadrature with 
the formal errors; the quoted errors in our labels already incorporate
these minimum errors.

@@

We also used the repeat observations to build intuition for the label
precision that was achievable as a function of S/N ratio.  Specifically
we stacked all spectra for a given star by summing the fluxes weighted
by the inverse variances, then treated the stacked spectra as a normal
survey star.  We inferred labels for the stacked spectra using all models,
and derived a joint estimate as per Section~\ref{sec:joining-the-models}.
The labels we inferred from the stacked spectrum serve as a basis of
comparison for the labels we derived from the individual visit spectra,
which are of lower S/N ratios.

@@

\begin{figure*}[p]
\caption{Distribution of differences in label estimates from multiple visits, divided by the quadrature sum of their formal errors, and a minimum error value for each observation.  If our measurements were unbiased and our errors were representative, no minimum error floor would be required and this distribution would by normally-distributed with zero mean and unity variance. 
We increased the error floor for a given label until the distribution variance approximately reached unity. The error floors are given for each label.\label{fig:pairwise-comparison}}
\end{figure*}

>>>>

We calculated all possible pair-wise differences between the labels we
derived from multiple visits.  If \rave\ observed a star $H$ times, there 
are $H!/2(H-2)!$ possible $a$-to-$b$ pair-wise combinations where we can calculate 
the difference between the derived label (for example, $\logg$) over the
quadrature sum of their formal uncertainties $(\logg_a - \logg_b)/\sqrt{{\sigma_{\logg,a}}^2 + {\sigma_{\logg,b}}^2}$.  If our derived labels and formal errors were 
correct, the distribution of these pair-wise comparisons would be
well-represented by a Gaussian distribution with zero mean and variance
of unity.  However, our formal errors are likely to be under-estimated,
and therefore we introduce a systematic error floor for each label, which
is added in quadrature to every observation such that (for example, $\logg$),
\begin{eqnarray}
	\eta_{\logg} & = & \frac{\logg_a - \logg_b}{\sqrt{(\sigma_{\logg,a} + \sigma_{\logg,floor})^2 + (\sigma_{\logg,b} + \sigma_{\logg,floor})^2}} \quad .
\end{eqnarray}

%\begin{eqnarray}
%\eta_{\logg} & = & \frac{\logg_a - \logg_b}{\sqrt{{\sigma_{\logg,a}}^2 + {\sigma_{\logg,b}}^2}} \quad .
%\end{eqnarray}

We increased the minimum label error until the distribution of $\eta$ 
values for a given label approximately reached unity.  The minimum error
values for each label are shown with the distribution of $\eta$
values in Figure \ref{fig:pairwise-comparison}.  These minimum values form
part of our error model, and \emph{have} been added in quadrature with 
the formal errors; the quoted errors in our labels already incorporate
these minimum errors.

@@

We further used the repeat observations in \rave\ to build intuition for
the label precision that was achievable as a function of S/N ratio.  
Specifically we stacked all spectra for a given star by summing the 
fluxes weighted by the inverse variances, then treated the stacked spectra
as a normal survey star.  We inferred labels for the stacked spectra 
using all three models, and derived a joint estimate as per Section 
\ref{sec:joining-the-models}.  The labels we inferred from the stacked 
spectrum then served as a basis of comparison for the labels we derived 
from the individual visit spectra of the same star, which are of lower 
S/N ratios.

@@

\begin{figure*}[p]
\includegraphics[width=\textwidth]{figures/pairwise-metrics.pdf}
\caption{Distribution of differences in label estimates from multiple visits, divided by the quadrature sum of their formal errors, and a minimum error value for each observation.  If our measurements were unbiased and our errors were representative, no minimum error floor would be required and this distribution would by normally-distributed with zero mean and unity variance. 
We increased the error floor for a given label until the distribution variance approximately reached unity. The error floors are given for each label.\label{fig:pairwise-comparison}}
\end{figure*}
